2H qSIP Calculations

### 2021-10-18 qSIP_calculations.Rmd
updated file path to include all new IRMS runs

```{r, warning=FALSE}
# set file path(s) to data files, folders or rds collections 
# can be multiple folders or mix of folders and files, using example data set here
data_path <- file.path("data", "IRMS", "2021-09-02_H_FAMES_TC")
ref_ratio <- get_standard("2H") %>% as.numeric()

>>>>

```{r, warning=FALSE}
# set file path(s) to data files, folders or rds collections 
# can be multiple folders or mix of folders and files
# setting the month of analysis folder - Isoverse will iteratively search subfolders. Huzzah! ^_^
data_path <- file.path("data", "IRMS", "2021-09")
ref_ratio <- get_standard("2H") %>% as.numeric()
